Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN normlaisation)

### 2017-08-06 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Minor bug fix

# Add in RIN^2 values
COVARIATES$RIN2 = COVARIATES$RIN^2
ContCovariates = c(ContCovariates, 'RIN2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=8}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
tmp = COVARIATES.CORRELATION$ESTIMATE
tmp[COVARIATES.CORRELATION$PVAL > 0.05] = 0
fdr = COVARIATES.CORRELATION$PVAL
fdr = format(fdr, digits=1)
h = Heatmap(tmp, col = colorRamp2(c(-1,0,1), c('blue','white','red')), name = 'AssocEstimate',
            cell_fun = function(j,i,x,y,wifht,height,fill){
                grid.text(fdr[i,j], x, y)
              })
draw(h, heatmap_legend_side = 'left', padding = unit(c(10,2,2,10), "mm"))
```

@@

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

@@

### Differential expression analysis (SCZ - Control)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=15, fig.width=20}
# Covariates to adjust
postAdjustCovars = adjust.covars

@@

### Associate differential expression results with gc content, gene length and average expression
```{r associate.de, fig.height=10, fig.width=15}
pl = list()
pl[[1]] = ggplot(DE %>% dplyr::filter(ref.Dx == 'Control', to.Dx == 'SCZ'), 
                 aes(x = log10(Length), y = logFC, color = Direction)) + geom_point() 
pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(Length), y = logFC))
pl[[1]] = pl[[1]] + facet_grid(ref.Tissue~.) + scale_color_manual(values = c('green','grey','red'))
pl[[1]] = pl[[1]] + theme(legend.position = 'top')

@@

### Differential expression analysis (Gender specific SCZ - Control)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp1, fig.height=15, fig.width=20}
# Covariates to adjust
COVARIATES$Dx.Tissue.Gender = factor(paste(COVARIATES$Dx.Tissue, COVARIATES$Gender, sep = '_'))
postAdjustCovars = c('Dx.Tissue.Gender', 'RIN', 'IntronicRate')

@@

### Differential expression analysis (ACC - DLPFC, SCZ - Control, Female - Male)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp2, fig.height=16, fig.width=8}
postAdjustCovars = c('Dx.Tissue', 'Gender', 'RIN', 'IntronicRate')

>>>>

# Add in RIN^2 values
COVARIATES$RIN2 = COVARIATES$RIN^2
ContCovariates = c(ContCovariates, 'RIN2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=15, fig.height=15}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
tmp = COVARIATES.CORRELATION$ESTIMATE
tmp[COVARIATES.CORRELATION$PVAL > 0.05] = 0
fdr = COVARIATES.CORRELATION$PVAL
fdr = format(fdr, digits=1)
h = Heatmap(tmp, col = colorRamp2(c(-1,0,1), c('blue','white','red')), name = 'AssocEstimate',
            cell_fun = function(j,i,x,y,wifht,height,fill){
                grid.text(fdr[i,j], x, y)
              })
draw(h, heatmap_legend_side = 'left', padding = unit(c(10,2,2,10), "mm"))
```

@@

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=12, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

@@

### Differential expression analysis (SCZ - Control)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=8, fig.width=8}
# Covariates to adjust
postAdjustCovars = c('Dx.Tissue', 'Gender', 'RIN', 'IntronicRate')

@@

### Associate differential expression results with gc content, gene length and average expression
```{r associate.de, fig.height= 6, fig.width = 12}
pl = list()
pl[[1]] = ggplot(DE %>% dplyr::filter(ref.Dx == 'Control', to.Dx == 'SCZ'), 
                 aes(x = log10(Length), y = logFC, color = Direction)) + geom_point() 
pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(Length), y = logFC))
pl[[1]] = pl[[1]] + facet_grid(ref.Tissue~.) + scale_color_manual(values = c('green','grey','red'))
pl[[1]] = pl[[1]] + theme(legend.position = 'top')

@@

### Differential expression analysis (Gender specific SCZ - Control)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp1, fig.height=6, fig.width=12}
# Covariates to adjust
COVARIATES$Dx.Tissue.Gender = factor(paste(COVARIATES$Dx.Tissue, COVARIATES$Gender, sep = '_'))
postAdjustCovars = c('Dx.Tissue.Gender', 'RIN', 'IntronicRate')

@@

### Differential expression analysis (ACC - DLPFC, SCZ - Control, Female - Male)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp2, fig.height=10, fig.width=6}
postAdjustCovars = c('Dx.Tissue', 'Gender', 'RIN', 'IntronicRate')
